A Non-local Bayesian Video Denoising Method

### 2015-11-12 doc/201507_tip/paper.tex
[doc] TIP paper: Updated PSNRs for grayscale sequences

\begin{figure}[htpb!]
	\centering
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
%	\vspace{.1cm}
	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
	the 20 nearest neighbors (top), the corresponding MAP estimates (middle) and the sample mean 
	and first 19 principal directions computed from the sample covariance matrix (bottom).
	For each image, each column corresponds to the 4 spatial slices of a $9\times9\times4$ patch.}
	\label{fig:patch_groups_patches}
\end{figure}

@@

			                      & V-BM4D-mp            & \Bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \Bsic{28.12} &       28.32   & \Bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \Bsic{28.89} &       29.37  & \Bsic{29.56} &       31.02   & \Bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \Bsic{27.81} &       29.37   & \Bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
										 & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline

@@

@@

	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details. \pcomment{NOTE: the values in the table need to be updated!!}}

>>>>

\begin{figure}[htpb!]
	\centering
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_045_085_012_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
	\vspace{.2cm}
	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_255_056_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
	\vspace{.2cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_orig.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_nisy.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_deno.png}\\
%	\vspace{.1cm}
%	\includegraphics[width = \columnwidth]{figs/patch_groups/patch_group_bus_110_090_010_s40_wx37_wt2_sx9_st4_r040_n200_pcas.png}\\
%	\vspace{.1cm}
	\caption{For each of the two sets of patches of Fig. \ref{fig:patch_groups_pos} we show
	the 20 nearest neighbors (top), the corresponding MAP estimates (middle) and the sample mean 
	and first 19 principal directions computed from the sample covariance matrix (bottom).
	For each image, each column corresponds to the 4 spatial slices of a $9\times9\times4$ patch.}
	\label{fig:patch_groups_patches}
\end{figure}

@@

			                      & V-BM4D-mp            & \bsic{34.32} &       34.95  & \Bsic{36.77} &       37.48   & \bsic{32.20} &       32.01   & \bsic{33.99} &       34.11  & \Bsic{37.58} &       37.85   & \bsic{33.47} &       33.68  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{33.16} &       33.65  & \bsic{34.69} &       35.43   & \bsic{30.74} &       31.47   & \bsic{32.18} &       33.00  & \bsic{36.75} &       38.14   & \bsic{33.21} &       33.98  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{34.49} &       35.01  & \bsic{36.02} &       36.82   & \bsic{32.26} &       33.15   & \bsic{34.05} &       34.87  & \bsic{37.36} & \Best{38.69}  & \bsic{33.70} & \Best{34.56} & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{34.89} &       35.49  & \bsic{36.40} &       37.40   & \bsic{32.70} &       33.49   & \bsic{34.68} &       35.47  & \bsic{37.30} & \Best{38.76}  & \Bsic{33.81} & \Best{34.64} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{35.03} &       35.70  & \bsic{36.35} &       37.63   & \Bsic{32.86} &       33.52   & \Bsic{34.91} &       35.73  & \bsic{37.06} & \Best{38.74}  & \Bsic{33.81} &       34.51  & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 1$     & \bsic{32.99} &       33.29  & \bsic{34.62} &       35.15   & \bsic{30.80} &       31.22   & \bsic{32.34} &       32.79  & \bsic{36.21} &       37.72   & \bsic{33.20} &       33.79  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \Bsic{34.35} &       34.68  & \bsic{35.87} &       36.62   & \bsic{32.41} &       32.92   & \Bsic{34.26} &       34.78  & \bsic{36.86} & \Best{38.55}  & \Bsic{33.73} & \Best{34.38} & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \Bsic{34.34} &       35.23  & \bsic{35.63} &       37.08   & \bsic{32.39} &       33.18   & \bsic{34.02} &       35.25  & \bsic{36.57} & \Best{38.45}  & \bsic{33.45} & \Best{34.36} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \Bsic{34.25} &       35.40  & \bsic{35.39} &       37.21   & \Bsic{32.54} &       33.10   & \bsic{34.03} &       35.48  & \bsic{36.05} &       38.27   & \bsic{33.39} &       34.10  & \bsic{todo } &       todo   \\\hline
%%			                      & VNLB   $s_t = 2$     & \bsic{34.33} &       34.62  & \Bsic{todo } &       todo    & \Bsic{todo } &       todo    & \bsic{34.44} &       34.67  & \Bsic{todo } &       todo    & \Bsic{33.82} & \Best{34.23} & \Bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 3$     & \Bsic{34.53} &       35.15  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{34.74} &       35.31  & \bsic{todo } & \Best{todo }  & \Bsic{33.81} & \Best{34.29} & \bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 4$     & \bsic{34.18} & \Best{35.32} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{34.41} & \Best{35.54} & \bsic{todo } &       todo    & \bsic{33.47} &       34.13  & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \bsic{30.54} &       31.08  & \Bsic{32.18} &       33.46   & \bsic{28.12} &       28.32   & \bsic{29.67} &       30.49  & \Bsic{33.62} &       34.54   & \bsic{29.04} &       29.69  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{29.60} &       30.32  & \bsic{30.74} &       31.71   & \bsic{26.10} &       26.81   & \bsic{27.79} &       28.64  & \bsic{32.40} &       33.82   & \bsic{28.64} &       29.46  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{30.81} &       31.54  & \bsic{32.01} &       33.24   & \bsic{27.84} &       28.64   & \bsic{29.63} &       30.63  & \bsic{33.20} &       35.05   & \bsic{29.28} &       30.19  & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{31.14} &       31.99  & \Bsic{32.23} &       33.81   & \bsic{28.33} &       29.18   & \bsic{30.27} &       31.38  & \bsic{33.09} &       35.29   & \Bsic{29.39} & \Best{30.35} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{31.19} &       32.22  & \bsic{32.05} &       34.07   & \Bsic{28.49} &       29.36   & \Bsic{30.47} &       31.74  & \bsic{32.72} & \Best{35.30}  & \Bsic{29.35} & \Best{30.35} & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 1$     & \bsic{29.62} &       30.16  & \bsic{30.76} &       31.54   & \bsic{26.17} &       26.56   & \bsic{27.89} &       28.39  & \bsic{32.41} &       33.77   & \bsic{28.69} &       29.26  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \Bsic{30.81} &       31.37  & \bsic{31.98} &       33.08   & \bsic{27.89} &       28.41   & \Bsic{29.69} &       30.41  & \bsic{33.17} & \Best{34.97}  & \Bsic{29.32} & \Best{30.00} & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{29.88} &       31.62  & \bsic{30.60} &       33.05   & \bsic{27.50} &       28.89   & \bsic{29.02} &       30.86  & \bsic{31.23} &       34.26   & \bsic{28.51} & \Best{30.08} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{29.49} &       31.64  & \bsic{30.10} &       32.94   & \bsic{27.47} &       29.07   & \bsic{28.86} &       31.12  & \bsic{30.51} &       33.88   & \bsic{28.26} & \Best{30.03} & \bsic{todo } &       todo   \\\hline
%%			                      & VNLB   $s_t = 2$     & \Bsic{30.73} &       31.24  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{29.83} &       30.34  & \Bsic{todo } & \Best{todo }  & \Bsic{29.38} &       29.90  & \Bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 3$     & \Bsic{30.82} &       31.66  & \bsic{todo } & \Best{todo }  & \bsic{todo } & \Best{todo }  & \Bsic{30.15} &       31.09  & \bsic{todo } & \Best{todo }  & \Bsic{29.33} & \Best{30.02} & \bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 4$     & \bsic{30.25} & \Best{31.69} & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{29.74} & \Best{31.35} & \bsic{todo } &       todo    & \bsic{28.89} & \Best{29.97} & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \bsic{28.89} &       29.37  & \bsic{29.56} &       31.02   & \bsic{25.63} &       26.20   & \bsic{26.73} &       27.99  & \Bsic{30.99} &       32.30   & \bsic{26.39} &       27.34  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{27.33} &       28.28  & \bsic{27.96} &       29.26   & \bsic{23.57} &       24.18   & \bsic{25.36} &       26.06  & \bsic{29.53} &       31.04   & \bsic{26.11} &       26.86  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{28.67} &       29.65  & \bsic{29.59} &       31.10   & \bsic{25.29} &       26.04   & \bsic{27.27} &       28.17  & \bsic{30.74} &       32.69   & \bsic{26.97} &       27.76  & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \bsic{29.12} &       30.13  & \Bsic{30.09} &       31.77   & \bsic{25.82} &       26.66   & \bsic{28.00} &       29.01  & \bsic{30.88} &       33.06   & \Bsic{27.17} & \Best{28.01} & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{29.26} &       30.38  & \Bsic{30.13} &       32.11   & \Bsic{26.04} &       26.93   & \Bsic{28.28} &       29.43  & \bsic{30.67} & \Best{33.19}  & \Bsic{27.20} & \Best{28.08} & \bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 1$     & \bsic{27.32} &       28.20  & \bsic{27.94} &       29.14   & \bsic{23.62} &       23.96   & \bsic{25.42} &       25.82  & \bsic{29.50} &       31.08   & \bsic{26.14} &       26.69  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{28.65} &       29.51  & \Bsic{29.55} &       30.93   & \bsic{25.33} &       25.78   & \Bsic{27.31} &       27.90  & \bsic{30.70} & \Best{32.63}  & \Bsic{26.99} &       27.55  & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{27.49} &       29.71  & \bsic{27.91} &       30.91   & \bsic{24.75} &       26.36   & \bsic{26.30} &       28.43  & \bsic{28.45} &       31.95   & \bsic{25.95} & \Best{27.72} & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{26.92} &       29.64  & \bsic{27.28} &       30.73   & \bsic{24.60} &       26.60   & \bsic{26.04} &       28.68  & \bsic{27.61} &       31.50   & \bsic{25.57} & \Best{27.71} & \bsic{todo } &       todo   \\\hline

@@

			                      & V-BM4D-mp            & \Bsic{27.67} &       28.38  & \bsic{27.81} &       29.37   & \bsic{23.68} &       24.59   & \bsic{24.64} &       26.02  & \Bsic{29.02} &       30.58   & \bsic{24.47} &       25.64  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 1$     & \bsic{25.66} &       26.82  & \bsic{26.01} &       27.53   & \bsic{21.85} &       22.37   & \bsic{23.53} &       24.25  & \bsic{27.37} &       28.97   & \bsic{24.27} &       25.05  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 2$     & \bsic{27.12} &       28.34  & \bsic{27.73} &       29.58   & \bsic{23.53} &       24.24   & \bsic{25.46} &       26.36  & \bsic{28.71} &       30.96   & \bsic{25.20} &       26.03  & \bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 3$     & \Bsic{27.60} &       28.84  & \bsic{28.30} &       30.32   & \bsic{24.09} &       24.90   & \bsic{26.16} &       27.26  & \bsic{28.92} &       31.42   & \Bsic{25.45} &       26.34  & \Bsic{todo } &       todo   \\
			                      & VNLB   $s_t = 4$     & \Bsic{27.75} &       29.11  & \Bsic{28.40} &       30.69   & \Bsic{24.31} &       25.19   & \Bsic{26.43} &       27.77  & \bsic{28.73} & \Best{31.57}  & \Bsic{25.50} & \Best{26.45} & \Bsic{todo } &       todo   \\\hline
%			                      & VNLB   $s_t = 1$     & \bsic{25.65} &       26.83  & \bsic{25.97} &       27.49   & \bsic{21.89} &       22.25   & \bsic{23.57} &       24.11  & \bsic{27.32} &       29.03   & \bsic{24.27} &       24.97  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 2$     & \bsic{27.09} &       28.27  & \bsic{27.67} &       29.46   & \bsic{23.56} &       24.06   & \Bsic{25.48} &       26.17  & \bsic{28.64} & \Best{30.90}  & \Bsic{25.21} &       25.89  & \bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 3$     & \bsic{25.66} &       28.33  & \bsic{25.93} &       29.31   & \bsic{22.84} &       24.65   & \bsic{24.35} &       26.69  & \bsic{26.31} &       30.11   & \bsic{24.11} & \Best{26.08} & \Bsic{todo } &       todo   \\
%			                      & VNLB   $s_t = 4$     & \bsic{24.98} &       28.16  & \bsic{25.18} &       29.03   & \bsic{22.62} &       24.89   & \bsic{23.98} &       26.90  & \bsic{25.41} &       29.59   & \bsic{23.64} & \Best{26.05} & \Bsic{todo } &       todo   \\\hline
%%			                      & VNLB   $s_t = 2$     & \bsic{27.14} &       28.15  & \bsic{todo } &       todo    & \bsic{todo } &       todo    & \bsic{25.43} &       26.06  & \bsic{todo } &       todo    & \bsic{25.18} &       25.81  & \bsic{todo } &       todo   \\
%%			                      & VNLB   $s_t = 3$     & \bsic{27.63} &       28.62  & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \bsic{26.15} &       26.94  & \Bsic{todo } & \Best{todo }  & \Bsic{25.44} & \Best{26.12} & \Bsic{todo } & \Best{todo } \\
%%			                      & VNLB   $s_t = 4$     & \Bsic{27.81} & \Best{28.86} & \Bsic{todo } & \Best{todo }  & \Bsic{todo } & \Best{todo }  & \Bsic{26.45} & \Best{27.46} & \Bsic{todo } & \Best{todo }  & \Bsic{25.50} & \Best{26.24} & \Bsic{todo } & \Best{todo } \\\hline

@@

% :r !for i in $(cat /media/pariasm/tera/funes/denoising/projects/video_nlbayes3d/results/vnlbayes/tip_table_1ps7_2ps7/te*/measures | grep PSNR_basic | sed ``s/^-PSNR_basic\ =\ ''//); do  echo ``scale=2;\left( (10^2)*$i)+0.5)/(10^2)'' | bc; done \right)

@@

	\caption{Quantitative denoising results for some classic grayscale test sequences. See text for details.}
